---
output: 
  html_document:
    output_dir: docs
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- 'docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning = FALSE)
library(tidyverse)
library(DT)
```

###  Comparative database of Permic varieties {.tabset .tabset-fade .tabset-pills}

#### About

This database accompanies the paper *On the questions in developing computational infrastructure for Komi-Permyak* by Rueter, Partanen & Ponomareva. The goal of that study was investigate the most central differences that must be accounted for when adapting Komi-Zyrian morphological analyser to work on Komi-Permyak. The features discussed in the paper are collected here into a database that can be extended later.

The data is shared under CC-0, in order to allow as unproblematic reuse as possible.

#### Search

```{r}

comparison <- read_csv("database.csv") %>%
  mutate(comment = case_when(is.na(comment) ~ "",
                             TRUE ~ as.character(comment)))
## In principle we could transform languages into columns too 
#  pivot_wider(names_from = language) %>%
#  select(Permyak, Zyrian, everything())
  
datatable(comparison, filter = 'top', rownames = FALSE, options = list(dom = 'tip'), escape = FALSE)
```
